Paper figures

### 2020-03-20 voltagebudget/analysis/paper_figures_lossy.Rmd
Tweak axis in Fig1-6 Other misc These are locked now

# Plot em....
p1 <- ref_times %>% 
  ggplot(aes(x=ts*1e3, y=ns)) +
  geom_point(alpha=0.8) +
  labs(x="Time (ms)", y="Neuron") +
  lims(x=c(0, 50)) +
  theme_classic() +
  ggtitle("Original\nmessage")

@@

p3 <- sync_times %>% 
  ggplot(aes(x=ts*1e3, y=ns)) +
  geom_point(alpha=0.8) +
  labs(x="Time (ms)", y="Neuron") +
  lims(x=c(0, 50)) +
  theme_classic() +
  ggtitle("Maximum\ncompression")

@@

## Figure 2 - error
```{r, message=FALSE, fig.height=0.95, fig.width=1}
p1 <- sync_times %>% 
  ggplot(aes(x=ts*1e3, y=ns)) +
  geom_point(alpha=0.8, size=1.2, shape=1) +
  geom_segment(aes(x=ts*ms, xend=(ts+delta)*ms, y=ns, yend=ns), 
               size=.4,
               color="palegreen4",
               alpha=0.99,
               # arrow=arrow(length = unit(.08, "npc")),
               lineend = 'round', 
               linejoin = 'round') +
  labs(x="Time (ms)", y="Neuron") +
  lims(x=c(0, 50)) +
  theme_classic() +
  ggtitle("Maximum\ncompression\nerror")

@@

# Plot
p1 <- monte_carlo_times %>% 
  ggplot(aes(x=ts*ms, y=ns)) +
  geom_point(alpha=0.8, shape=1) +
  geom_segment(aes(x=ts*ms, xend=(ts+delta)*ms, y=ns, yend=ns), 
               size=.6,
               color="palegreen4",
               alpha=0.99,
               # arrow=arrow(length = unit(.08, "npc")),
               lineend = 'round', 
               linejoin = 'round') +
  facet_wrap(~exp) +
  labs(x="Time (ms)", y="Neuron") +
  lims(x=c(0, 50)) +
  theme_classic() +
  theme(
    legend.position="none", 
    panel.border = element_rect(fill = NA, colour = "grey"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    strip.text.y = element_text(angle = 0)) +
  ggtitle("Random\ncompression (10%)")

p2 <- monte_carlo_results %>% 
  ggplot(aes(x=(errors - mean(errors))*ms)) +
  geom_histogram(alpha=0.4, fill="palegreen4") +
  # geom_histogram(alpha=0.8, bins=30, binwidth = .01) +
  geom_density(alpha=0.8, color="palegreen4") +
  labs(y="Count", x="Error (ms)") +
  lims(x=c(-0.25, 0.25)) +
  theme_classic()

p3 <- monte_carlo_results %>% 
  ggplot(aes(x=(obs_variances - mean(obs_variances))*ms)) +
  geom_histogram(alpha=0.4) +
  geom_density(alpha=0.8) +
  labs(y="Count", x="Synchrony (ms)") +
  lims(x=c(-0.25, 0.25)) +
  theme_classic()

p1 / (p3 + p2 + plot_spacer()) + 
  plot_layout(heights = c(3, 1)) + 
  plot_annotation(tag_levels = 'a', tag_suffix = ".")

@@

# Plot....
optimal_times %>% 
  ggplot(aes(x=ts*ms, y=ns)) +
  geom_point(size=1.2, alpha=0.8, shape=1) +
  geom_segment(aes(x=ts*ms, xend=(ts+delta)*ms, y=ns, yend=ns, color=alg), 
               size=.6,
               alpha=0.8,
               # arrow=arrow(length = unit(.08, "npc")),
               lineend = 'round', 
               linejoin = 'round') +
  facet_grid(alg~.) +
  scale_color_manual("Algorithm:", values=c("darkslategray4", "darkseagreen3", "chartreuse3")) +
  theme_classic() +
  labs(x="Time (ms)", y="Neuron") +
  ggtitle("Optimal\ncompression") +
  theme(
    legend.position="none", 
    panel.border = element_rect(fill = NA, colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text.y = element_text(angle = 0)) -> p1

optimal_results %>% 
  filter(alg != "left") %>%
  filter(obs_variances > 10e-3) %>% 
  ggplot(aes(x=errors*1e3, y=obs_variances*1e3, color=alg)) +
  # geom_line(size=0.1, alpha=0.99) +
  geom_line(size=1, alpha=0.99) +
  scale_color_manual("Algorithm", 
                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
                     guide = guide_legend(nrow = 3)) +
  theme_classic() +
  coord_flip() +
  labs(x="Time (ms)", y="Neuron") +
  theme(legend.position="none",
    legend.key.size = unit(.1, "cm"),
    legend.title = element_text(size=6),
    legend.text = element_text(size=6),
    legend.background = element_rect(colour ="black")) +
  labs(x="Error (ms)", y="Synchrony (ms)") -> p2

@@

# Plot....
opt_v_osc_results %>% 
  filter(errors_pop > 0, freq %in% c("8")) %>%
  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms)) +
  geom_point(size=0.2, alpha=0.99) + 
  geom_point(mapping=aes(x=variances_opt*ms, y=errors_opt*ms, color=alg), 
             alpha=0.99, size=0.6) +
  scale_y_continuous(trans='log10') +
  annotation_logticks(sides = "l") +
  # facet_grid(freq~., labeller=hospital_labeller) +
  scale_color_manual("Algorithm", 
                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
                     guide = guide_legend(nrow = 3)) +
  labs(x="Synchrony (ms)", y="Error (ms)") +
  scale_x_continuous(breaks=c(7.5,8,8.5,9)) +
  ggtitle("Optimal versus\noscillation") +
  theme_classic() +
  theme(legend.position="right",
    legend.key.size = unit(.1, "cm"),
    legend.title = element_text(size=6),
    legend.text = element_text(size=6),
    legend.background = element_rect(colour ="black"),
    strip.text.y = element_text(angle = 0), 
    panel.grid.minor = element_blank(),
    legend.key.width=unit(0.05,"cm"),
    strip.background = element_blank()) -> p1

opt_v_osc_results %>% 
  filter(errors_pop > 0, freq %in% c("8")) %>%
  ggplot(aes(x=variances_pop*ms, y=variances_opt*ms, color=alg)) +
  geom_point(size=0.8, alpha=0.3) +
  geom_abline(intercept = 0, color="black", alpha=1) +
  labs(x="Oscillation\nsynchrony (ms)", y="Optimal\nsynchrony (ms)") +
  scale_color_manual("Algorithm:", 
                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
                     guide = "none") +
  theme_classic() +
  theme(plot.title = element_text(size = 10)) -> p2

@@

# Figure 6 - osc freq v optimal
```{r, fig.width=2, fig.height=3, message=FALSE}
# Plot....
opt_v_osc_results %>% 
  filter(errors_pop > 0, freq %in% c("8","12","20","30")) %>%
  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms)) +
  geom_point(size=0.2, alpha=0.99) + 
  geom_point(mapping=aes(x=variances_opt*ms, y=errors_opt*ms, color=alg), 
             alpha=0.99, size=0.6) +
  scale_y_continuous(trans='log10') +
  annotation_logticks(sides = "l") +
  facet_grid(freq~., labeller=hospital_labeller) +
  scale_color_manual("Algorithm", 
                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
                     guide = guide_legend(nrow = 3)) +
  labs(x="Synchrony (ms)", y="Error (ms)") +
  scale_x_continuous(breaks=c(7.5,8,8.5,9)) +
  ggtitle("Optimal versus\nfrequency") +
  theme_classic() +
  theme(legend.position="right",
    legend.key.size = unit(.1, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    legend.background = element_rect(colour ="black"),
    strip.text.y = element_text(angle = 0), 
    panel.grid.minor = element_blank(),
    legend.key.width=unit(0.05,"cm"),
    strip.background = element_blank()) -> p1

>>>>

# Plot em....
p1 <- ref_times %>% 
  ggplot(aes(x=ts*1e3, y=ns)) +
  geom_point(alpha=0.8, size=0.6) +
  labs(x="Time (ms)", y="Neuron") +
  lims(x=c(0, 50)) +
  theme_classic() +
  ggtitle("Original\nmessage")

@@

p3 <- sync_times %>% 
  ggplot(aes(x=ts*1e3, y=ns)) +
  geom_point(alpha=0.8, size=0.6) +
  labs(x="Time (ms)", y="Neuron") +
  lims(x=c(0, 50)) +
  theme_classic() +
  ggtitle("Maximum\ncompression")

@@

## Figure 2 - error
```{r, message=FALSE, fig.height=0.95, fig.width=1}
p1 <- sync_times %>% 
  ggplot(aes(x=ts*1e3, y=ns)) +
  geom_segment(aes(x=ts*ms, xend=(ts+delta)*ms, y=ns, yend=ns), 
               size=.4,
               color="palegreen4",
               alpha=0.8,
               # arrow=arrow(length = unit(.08, "npc")),
               lineend = 'round', 
               linejoin = 'round') +
  geom_point(alpha=0.8, size=0.6) +
  labs(x="Time (ms)", y="Neuron") +
  lims(x=c(0, 50)) +
  theme_classic() +
  ggtitle("Maximum\ncompression\nerror")

@@

# Plot
p1 <- monte_carlo_times %>% 
  ggplot(aes(x=ts*ms, y=ns)) +
  geom_segment(aes(x=ts*ms, xend=(ts+delta)*ms, y=ns, yend=ns), 
               size=.6,
               color="palegreen4",
               alpha=0.8,
               # arrow=arrow(length = unit(.08, "npc")),
               lineend = 'round', 
               linejoin = 'round') +
  geom_point(alpha=0.8, size=0.6) +
  facet_wrap(~exp) +
  labs(x="Time (ms)", y="Neuron") +
  lims(x=c(0, 50)) +
  theme_classic() +
  theme(
    legend.position="none", 
    panel.border = element_rect(fill = NA, colour = "grey"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    strip.text.y = element_text(angle = 0)) +
  ggtitle("Random\ncompression (10%)")

p2 <- monte_carlo_results %>% 
  ggplot(aes(x=(errors - mean(errors))*ms)) +
  geom_histogram(alpha=0.4, fill="palegreen4") +
  # geom_histogram(alpha=0.8, bins=30, binwidth = .01) +
  geom_density(alpha=0.8, color="palegreen4") +
  labs(y="Count", x="Error\nvariance (ms)") +
  lims(x=c(-0.25, 0.25)) +
  theme_classic()

p3 <- monte_carlo_results %>% 
  ggplot(aes(x=(obs_variances - mean(obs_variances))*ms)) +
  geom_histogram(alpha=0.4) +
  geom_density(alpha=0.8) +
  labs(y="Count", x="Compression\nvariance (ms)") +
  lims(x=c(-0.25, 0.25)) +
  theme_classic()

p1 / (p3 + p2) + 
  plot_layout(heights = c(3, 1)) + 
  plot_annotation(tag_levels = 'a', tag_suffix = ".")

@@

# Plot....
optimal_times %>% 
  ggplot(aes(x=ts*ms, y=ns)) +
  geom_segment(aes(x=ts*ms, xend=(ts+delta)*ms, y=ns, yend=ns, color=alg), 
               size=.6,
               alpha=0.8,
               # arrow=arrow(length = unit(.08, "npc")),
               lineend = 'round', 
               linejoin = 'round') +
  geom_point(alpha=0.8, size=0.6) +
  facet_grid(alg~.) +
  scale_color_manual("Algorithm:", values=c("darkslategray4", "darkseagreen3", "chartreuse3")) +
  theme_classic() +
  labs(x="Time (ms)", y="Neuron") +
  ggtitle("Optimal\ncompression") +
  theme(
    legend.position="none", 
    panel.border = element_rect(fill = NA, colour = "black"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_blank(),
    strip.text.y = element_text(angle = 0)) -> p1

optimal_results %>% 
  filter(alg != "left") %>%
  filter(obs_variances > 10e-3) %>% 
  ggplot(aes(x=errors*1e3, y=obs_variances*1e3, color=alg)) +
  geom_line(size=1, alpha=0.8) +
  scale_color_manual("Algorithm", 
                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
                     guide = guide_legend(nrow = 3)) +
  theme_classic() +
  coord_flip() +
  labs(x="Time (ms)", y="Neuron") +
  theme(legend.position="none",
    legend.key.size = unit(.1, "cm"),
    legend.title = element_text(size=6),
    legend.text = element_text(size=6),
    legend.background = element_rect(colour ="black")) +
  labs(x="Error (ms)", y="Compression (ms)") -> p2

@@

# Plot....
opt_v_osc_results %>% 
  filter(errors_pop > 0, freq %in% c("8")) %>%
  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms)) +
  geom_point(size=0.2, alpha=0.99) + 
  geom_point(mapping=aes(x=variances_opt*ms, y=errors_opt*ms, color=alg), 
             alpha=0.99, size=0.4) +
  scale_y_continuous(trans='log10') +
  annotation_logticks(sides = "l") +
  # facet_grid(freq~., labeller=hospital_labeller) +
  scale_color_manual("Algorithm", 
                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
                     guide = guide_legend(nrow = 3)) +
  labs(x="Compression (ms)", y="Error (ms)") +
  scale_x_continuous(breaks=c(7.5,8,8.5,9)) +
  ggtitle("Optimal versus\noscillation") +
  theme_classic() +
  theme(legend.position="right",
    legend.key.size = unit(.1, "cm"),
    legend.title = element_text(size=6),
    legend.text = element_text(size=6),
    legend.background = element_rect(colour ="black"),
    strip.text.y = element_text(angle = 0), 
    panel.grid.minor = element_blank(),
    legend.key.width=unit(0.05,"cm"),
    strip.background = element_blank()) -> p1

opt_v_osc_results %>% 
  filter(errors_pop > 0, freq %in% c("8")) %>%
  ggplot(aes(x=variances_pop*ms, y=variances_opt*ms, color=alg)) +
  geom_point(size=0.8, alpha=0.3) +
  geom_abline(intercept = 0, color="black", alpha=1) +
  labs(x="Oscillation\ncompression (ms)", y="Optimal\ncompression (ms)") +
  scale_color_manual("Algorithm:", 
                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
                     guide = "none") +
  theme_classic() +
  theme(plot.title = element_text(size = 10)) -> p2

@@

# Figure 6 - osc freq v optimal
```{r, fig.width=2, fig.height=3, message=FALSE}
# Plot....
opt_v_osc_results %>% 
  filter(errors_pop > 0, freq %in% c("8","12","20","30")) %>%
  ggplot(aes(x=variances_pop*ms, y=errors_pop*ms)) +
  geom_point(size=0.2, alpha=0.99) + 
  geom_point(mapping=aes(x=variances_opt*ms, y=errors_opt*ms, color=alg), 
             alpha=0.99, size=0.6) +
  scale_y_continuous(trans='log10') +
  annotation_logticks(sides = "l") +
  facet_grid(freq~., labeller=hospital_labeller) +
  scale_color_manual("Algorithm", 
                     values=c("darkslategray4", "darkseagreen3", "chartreuse3"),
                     guide = guide_legend(nrow = 3)) +
  labs(x="Compression (ms)", y="Error (ms)") +
  scale_x_continuous(breaks=c(7.5,8,8.5,9)) +
  ggtitle("Optimal versus\nfrequency") +
  theme_classic() +
  theme(legend.position="right",
    legend.key.size = unit(.1, "cm"),
    legend.title = element_text(size=8),
    legend.text = element_text(size=8),
    legend.background = element_rect(colour ="black"),
    strip.text.y = element_text(angle = 0), 
    panel.grid.minor = element_blank(),
    legend.key.width=unit(0.05,"cm"),
    strip.background = element_blank()) -> p1
